Approximate State Abstraction

### 2016-01-29 paper/paper.tex
Q* proof done first pass -- still need to do t=1 case for heterogeneous MDP.

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand\defn[1]{{\bf Definition:} #1}

@@

%\begin{align*}
%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \\ &\max_a \left[\sum_{g \in s} R_{G}(g,a)\omega(g) + \gamma \sum_{s'} \sum_{g \in s}T_G(g,a,s')\omega(g)V_0(s') \right] \\
%&= \gamma\left(\sum_{t=0}^{T-1}\epsilon\gamma^t\right) + \epsilon + \left(\max_a Q_G(s,a)\right) \\
%&= \sum_{t=0}^{T} \epsilon \gamma^{t} + \max_a Q^{\pi_G^*}(s,a) \\
%&= \frac{\epsilon}{1-\gamma} + V^{\pi_G^*}(s) \\
%\end{align*}

@@

max

@@

@@

\begin{align*}
\text{Let }Q^{\pi_{A,t}}(g) &= \\
&R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')
\end{align*}

@@

We now show by induction on $t$ that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t}\gamma^i \frac{\epsilon}{1-\gamma}
\end{equation}

@@

By definition when $t=0$, $Q^{\pi_{A,t}} = Q^{\pi^*}$ so it trivially follows that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,0}}(g, a) \leq Q^{\pi^*}(g,a) + \frac{\epsilon}{1-\gamma}
\end{equation}

@@

We assume for our inductive hypothesis that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g, a} Q^{\pi_{A,t-1}}(g, a) \leq Q^{\pi^*}(g,a) + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma}
\end{equation}

By definition 
\begin{align*}
&Q^{\pi_{A,t}}(g, a) = R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi_{A,t-1}}(g', a')\\
&\text{Applying our inductive hypothesis yields}\\
&Q^{\pi_{A,t}}(g, a) \leq\\
&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}\left(Q^{\pi^*}(g',a') + \sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} \right)\\
&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\max_{a'}Q^{\pi^*}(g',a')\\
&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
&\text{Applying Equation \ref{} yields}\\
&\leq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{\epsilon}{1-\gamma} + Q^{\pi^*}(g, a)\\
\end{align*}
% Subsection: Model Similarity
\subsection{Model Similarity: $\ep_{model}$}

>>>>

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand\defn[1]{{\bf Definition:} #1}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

@@

@@

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$ and its corresponding abstract state $s_A=\epQ(s_G)$.

Let $a^*_G$ stand for the optimal action for $s_G$: \\
$a^*_G = \argmin Q_G(s_G, a)$

Let $a^*_A$ stand for the optimal action for $s_A$:\\
 $a^*_A = \argmin Q_A(s_A, a)$

By Equation \ref{eq:Q*HalfResult} and the definition of $a^*_G$ and $a^*_A$ we know that 
\begin{align}
&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma} \nonumber \\
\label{eq:Q*OptActionResult}
&\leq Q_A(s_A, a^*_A) + \frac{\epsilon}{1-\gamma} \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
\end{align}

@@

Again, consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$

\begin{align*}
\text{Let }V^{\pi_{A,t}}(s_G) &= \\
&R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')
\end{align*}

@@

%Start induction on following the optimal abstract policy
We now show by induction on $t$ that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

By definition when $t=0$, $V^{\pi_{A,t}} = V^{\pi^*}$ so it trivially follows that
\begin{equation}
V^{\pi^*}(s_G) \leq V^{\pi_{A,0}}(s_G) + \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

We assume for our inductive hypothesis that
\begin{equation}
V^{\pi^*}(s_G) \leq V^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

By definition 
\begin{align*}
&V^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V^{\pi_{A,t-1}}({s_G}')\\
&\text{Applying our inductive hypothesis yields}\\
&V^{\pi_{A,t}}(g, a) \geq\\
&R_G(s, \pi_{A,t}(g, a)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')\left(V^{\pi^*}({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q^{\pi^*}(g, \pi_{A,t} (g))\\
&\text{Applying Equation \ref{eq:Q*OptActionResult} yields}\\
&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(g)\\
& \text{Thus,}\\
&V^{\pi^*}(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{align*}

From our base case and induction we conclude that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of a geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.

Thus we conclude,
\begin{equation*}
\forall_{g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A}^*}(g) + \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

\begin{equation*}
\forall_{g \in \mathcal{S}_g} \left | V^{\pi^*}(g) - V^{\pi_{A}^*}(g) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

% Subsection: Model Similarity
\subsection{Model Similarity: $\ep_{model}$}
